---
title: "Untitled"
output: html_document
---


. Load in all the layers
. Subset data
. Represent as vector
. bind vectors of each layer into single frame of multiple features
. Train on outcome

. Classify for whole image
. Overalay shape files
. Classify areas as conflict or not.
. Calculate local percentage conflict and local tonnage.

Additional Ideas
. Likely owner
. Expansion Risk
. Time of expansion

##Useful websites for feature engineering
http://landsat.usgs.gov/band_designations_landsat_satellites.php

http://www.harrisgeospatial.com/Learn/WhitepapersDetail/TabId/802/ArtMID/2627/ArticleID/13742/Vegetation-Analysis-Using-Vegetation-Indices-in-ENVI.aspx

http://web.pdx.edu/~emch/ip1/bandcombinations.html



```{r}
packages <- c("tidyverse", "rgdal", "raster", "gridExtra", "caret","randomForest","xgboost", "e1071", "snow", "RColorBrewer", "rgeos", "xtable", "RStoolbox", "forcats")

#This piece of code will check to see if the packages you want to load are installed if they aren't it will install them
new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

invisible(sapply(packages, library, character.only = TRUE))

#save the starting directory as a variable
basewd <-getwd()

select <-dplyr::select

mode<-"cloud"

if(mode == "cloud"){
  palmbase <-"~/Dropbox/PalmOil"
  TIFF <- "~/Dropbox/PalmOil/Tiff"
  forestshapefile <- "~/Dropbox/PalmOil/ForestShape"
  palmconc<-"~/Dropbox/PalmOil/palmconc"
} else {
  palmbase <-"~/Dropbox/PalmOil"
  TIFF <- "C:/Users/Gail/Desktop/TiffTest"
  }

setwd(palmbase)
```


Function used later in the analysis
```{r}
#Compresses a data frame to the mean value of a square set of cells in a dataframe
#df = A datframe
#merge = the number of cell in the x and y direction to merge
#Requires dplyr 

CompressDf <-function(df,merge = 5){
  
  print("Compressing data along rows")
  
  totrows <-nrow(df)
  remainder <- merge-(totrows %%merge)
  numgroups <-(totrows +remainder)/merge
  
  #rearrange dataframe columns and aggreagte into the predefined groups of size merge
  #rows and columns are first ordered by similarity
  test <- df%>% as.data.frame %>%
    mutate(rowID =rep(1:numgroups,each=merge)[1:totrows]) %>%
    group_by(rowID) %>% summarise_all(funs(mean)) %>%
    select(-rowID) #add in -rows again is the rows data is commented back in
  
  print("Compressing data along Columns")
  #allows the grouping to be flexible in the case that the dataframe changes size
  totcols <-ncol(test)
  remainder <- merge-(totcols %%merge)
  numgroups <-(totcols +remainder)/merge
  
  
  #aggregate again transposing the data frame and aggregating by the smart meters
  test <- t(test) %>% data.frame %>% 
    mutate(rowID =rep(1:numgroups,each=merge)[1:totcols]) %>%
    group_by(rowID) %>% summarise_all(funs(mean)) %>%select(-rowID) %>%
    t %>% data.frame %>% mutate( rowID = 1:nrow(.)) 
  
}
```


```{r CorrectCreate}
#This function correct for reflectance and creates the new variables.



ReflectCorrect <-function(df, Band, meta ){
  Var <- eval(parse(text = paste0("df$B",Band)))
  #The names cannot have whitespace which may happen on some loading.
  MultPart  <- meta$L1_METADATA_FILE[grep(paste0("REFLECTANCE_MULT_BAND_",Band),meta$GROUP)] %>% as.numeric
  AddPart<- meta$L1_METADATA_FILE[grep(paste0("REFLECTANCE_ADD_BAND_",Band),meta$GROUP)]%>% as.numeric
  
  #Sun elevations to be converted to radians
  SunElev <- meta$L1_METADATA_FILE[grep("SUN_ELEVATION",meta$GROUP)] %>% as.numeric *(2*pi/360)
  RefCor <- MultPart*Var + AddPart
  RefCor <- RefCor/sin(SunElev)
  return(RefCor)
  }


CorrectCreate <- function(df, meta){
  
  #Corrects for the reflectance of the variables using the metadata
  
  df2 <- df %>% select(-Class,-B10,-B11)

  df <- lapply(grep("^B",names(df2)), function(n){
    print(n)
      data_frame(Var = (ReflectCorrect(df2, n, meta) )) %>%
        setNames(paste0("CB",n))
    }
  ) %>%  bind_cols %>% bind_cols(., df)

#  df<- df %>% setNames(ifelse(grepl("^B",names(df)), paste0("C",names(df)) ,names(df)))  
    
  #Creates the new variables from the corrected variables
  df <- df %>% mutate(TNDVI = sqrt(((CB5-CB4)/(CB5+CB4))+1), 
                                  ForCrop1 = CB3/CB2,
                                  ForCrop2 = CB7/CB2,
                                  WatLan1 = CB6/CB7,
                                  WatLan2= (CB4+CB5)/(CB6*2),
                                  SAVI = ((CB5-CB4)/(CB5+CB4+0.5))*(1+0.5),
                                  Tassel_B = 0.3029*CB2 +0.2786*CB3 + 0.4733*CB4+0.508*CB6+0.1872*CB7,
                                  Tassel_G = -0.2941*CB2 -0.243*CB3-0.5424*CB4+0.7276*CB5+0.0713*CB6-0.1608*CB7,
                                  Tassel_W = 0.1511*CB2+0.1973*CB3+0.3283*CB4+0.3407*CB5-0.7117*CB6-0.4559*CB7,
                                  EVI = 2.5*(CB5-CB4)/(CB5+6*CB4-7.5*CB2+1))
}

```


```{r}
CreateTiffFrame <- function(img, trainData, responseCol){
 #This function outputs a data frame with a column for the pixel data and a column for the output variable, for a stacked raster it will include a column for each band
  
TiffFrame <- lapply(1:length(unique(trainData[[responseCol]])), function(i){    
          category <- unique(trainData[[responseCol]])[i]
          categorymap <- trainData[trainData[[responseCol]] == category,]
          dataSet <- extract(img, trainData[trainData[[responseCol]] == category,] )
          dataSet <- lapply(dataSet, as.data.frame) %>% bind_rows %>% mutate( Class = category)
          }) %>% bind_rows()
}
```


```{r}
CompressAndPlot<- function(df, merge = 10, Catags, CatColours){


df2 <- 0:(length(Catags)) %>% map(~{
  #finds the probability of each class per pixel and assembles into a dataframe
  n <-. 
  ((df==(n))*1) %>% CompressDf(., merge) %>%
    gather(.,key = "columnID", value =Percentvalid, -rowID )%>%
    mutate(columnID = sub("X","", columnID) %>% as.integer) %>% 
    data.frame %>% setNames(c(names(.)[1:2], paste0("Type", n)))
  }
  ) %>% Reduce(function(dtf1,dtf2) left_join(dtf1,dtf2,by=c("columnID", "rowID")), .) %>% #turn list to dataframe
  mutate(Type = Catags[max.col(.[3:ncol(.)])], #find most prevelant type
         Type = Type %>% as.factor %>% 
           fct_relevel("Empty"),
         Type = fct_relevel(Type, "Conflict", after = Inf), Type) #re-order factor levels
  


#plot with the conflict level included
ggplot(df2, aes(y=-rowID, x= columnID, fill = Type )) +
    geom_raster() +scale_fill_manual(values = CatColours)+#theme_bw() +
    coord_equal() + labs(title = "Areas of conflict palm") + 
    theme(axis.title= element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    legend.key = element_blank(),
    plot.title = element_text(hjust = 0.5)) 
}

```


untar data
```{r}
setwd(TIFF)

#all above band 7 is corrupted or something, band bQA is nothing 
files <- list.files(pattern =".TIF")

#finds the correct bands and orders them correctly
filewant <- files %>% sub("LC81190622016273LGN00_B", "", .) %>% 
  sub(".TIF", "", .) %>% as.numeric %>% base::match(c(1:7,10,11), .)

LSI<- lapply(files[filewant], brick)%>% stack  %>%
  setNames(sub(".+_", "", names(.))) 

meta <- read_delim("LC81190622016273LGN00_MTL.txt"    , delim = "=") %>% 
  setNames(trimws(names(.)))
```




```{r PlotMap}
setwd(palmbase)
 ggRGB(LSI, r=4,g=3,b=2) + labs(title = "The original satellite image shown in natural colours") +
             theme(axis.title= element_blank(),
                axis.text = element_blank(),
                axis.ticks = element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                legend.position = "right",
                legend.key = element_blank(),
                plot.title = element_text(hjust = 0.5))
ggsave("BaseImage.png")
```



```{r ExtractTrainingData}


#setwd(forestshapefile)
#trainData <- shapefile("ForestLC8119.shp")

setwd(palmbase)
trainData <- shapefile("ClassShapes050417.shp")


#Tiff2 has correction
#Tiff3 has no correction

if (!file.exists(file.path(palmbase, "TiffFrameRaw.RDS"))){
TiffFrame <- CreateTiffFrame(LSI, trainData, "Class")

 saveRDS(TiffFrame,"TiffFrameRaw.RDS")
 } else {
  setwd(palmbase)
    TiffFrame <- readRDS("TiffFrameRaw.RDS")
   
 }
#tassel and savi from here
#http://grindgis.com/blog/vegetation-indices-arcgis#1

```


```{r Process}

TiffFrame <- TiffFrame %>% CorrectCreate(., meta)


```



```{r CreateModel}

TiffFrame <- TiffFrame %>% filter(Class!="Urban") #%>% select(-SAVI, -B10,-B11,-Tassel_B,-Tassel_G,-Tassel_W,-EVI)

Classdf <- data.frame(Class = TiffFrame$Class) %>% 
  mutate(ClassNum =  Class %>% 
           as.factor %>% 
           as.numeric -1)  #Classes have to start at 0

ClassCodes <- unique(Classdf)

set.seed(1987)
 trainvect<- sample(1:nrow(TiffFrame), 0.8*nrow(TiffFrame))

 Tiffmat<-as.matrix(select(TiffFrame, -Class))

 #modelversion 
 #Mod1 was the original model 
 #Mod2 includes SAVI and TASSEL and EVI The model couldn't differentiate water for some reason
 #Mod3 Extra water in training data
 
 mod <- "Mod4.rds"
 
if (!file.exists(file.path(palmbase, mod))){
 Mod1 <- xgboost(Tiffmat[trainvect,],
        label = Classdf$ClassNum[trainvect],
                    max.depth=6,
                    eta = 0.30,
                    nround = 50,
                    objective = "multi:softmax",
                    num_class = length(unique(Classdf$ClassNum)),
                    eval_metric ="merror",
                    missing="NAN")

#save model as it takes a long time to build
setwd(palmbase)

saveRDS(Mod1, mod) 
} else {

  Mod1 <-  readRDS(file.path(palmbase, mod))
}

Preds1 <- predict(Mod1, Tiffmat[-trainvect,], missing="NAN")
confusionMatrix(Preds1, Classdf$ClassNum[-trainvect])

importance <- xgb.importance(feature_names = colnames(Tiffmat), model = Mod1)

#these are no longer needed and are quite large so should be removed
rm(Tiffmat)
rm(TiffFrame)
gc()

setwd(palmbase)
importance %>%  mutate(Feature = factor(Feature, levels = Feature[order(-importance$Gain)])) %>% 
  ggplot(., aes(x = Feature, y = Gain)) +geom_bar(stat="identity") +
  ggtitle("Variable Importance for classification\nof rural Indonesia using Landsat 8 Images")
#ggsave("VarImp.png")
```



```{r}


SplitByRow <- function(df, rowspergroup, fun,...){
  totrows <- nrow(df)
  remainder <- rowspergroup - (totrows %%rowspergroup)
  numgroups <- (totrows +remainder)/rowspergroup

  df2 <- df %>% mutate(rowID =rep(1:numgroups,each=rowspergroup)[1:totrows]) %>%
    split(.$rowID) %>%
    map(~eval(parse(text=fun)))
    
  
}

ProcessPredict <- function(df, meta, Mod) {
    df %>% mutate_all(as.numeric) %>% mutate(Class = NA) %>%
      CorrectCreate(., meta) %>% 
      select(-Class) %>%
      as.matrix %>%
      predict(Mod, ., missing = 'NAN')
    }
  
fun <- "ProcessPredict(.,meta, Mod1)"

predmatfile <- "predmataLL2.RDS"

if(!file.exists(file.path(palmbase, predmatfile))){

    #Convert entire image
    print("Converting Image")
    predmat <-as.data.frame(LSI) 
    
    #predict class of whole image
    print("Splitting by rows")
    predmat <-  SplitByRow(predmat, nrow(predmat)/100, fun) 
    
    print("Converting to integer vector")
    predmat<- predmat %>% map(as.integer) %>%  unlist(use.names=FALSE)
    
    #Change the prediction vector back into a raster image.
    print("converting to matrix")
    predmat <- matrix(predmat, nrow= 7771, byrow = TRUE) %>% as.data.frame
    saveRDS(predmat, predmatfile)
    
  }else{
    setwd(palmbase)
    predmat <- readRDS(predmatfile)
  }

predmat <- as.data.frame(predmat)

Catags <-c("Cloud", "Empty", "Forest", "Plantation", "Water" )
CatColours <- c("black", "white", "darkgreen", "green", "blue")

z <- CompressAndPlot(predmat, 10, 
                c("Cloud", "Empty", "Forest", "Plantation", "Water" ),
                c("black", "white", "darkgreen", "green", "blue"))
 # ggsave("ModMap.png")

```


extract  useful stats from the matrix

. 1 pixel is equivalent to 0.009 hectares of land
. 1 hectare of land can produce 3.69 tonnes per hectare.
. 1km^2 is equal to 100 hactares
```{r}
px <- sapply(0:4, function(n) sum(predmat ==n))
ppt <-780 #price per tonne

imagedata <- ClassCodes %>% arrange(ClassNum) %>% mutate(pixels = px, km2 = round(pixels * 9e-5))
imagedata

#Tonnes of Palm Oil Equivalent

TonnesOil <- imagedata$km2[imagedata$Class== "Plantation"] * 3.69*100
#value of oil in USD

TonnesOil*ppt/1e6

```


```{r IdentifyConlfict}
#load concessions
setwd(palmconc)
IndoPalmConc <- shapefile("Indonesia_oil_palm_concessions.shp")
IndoPalmConc <- spTransform(IndoPalmConc,CRS=crs(LSI))

predrast <- raster(predmat)
extent(predrast) <- extent(LSI)

#This calculation takes  a long time if you don't need to do it multiple times it's better
if(!file.exists(file.path(palmbase,"LegalPlantationMask.rds"))){

  maskrast<- matrix(1:length(predmat), nrow = 7771) %>% raster
  
  extent(maskrast) <- extent(LSI)

  LegalPlantationMask <- extract(maskrast, IndoPalmConc) %>% 
  lapply(., as.data.frame) %>% bind_rows

  LegalPlantationMask <- LegalPlantationMask[,1] %>% as.integer
  
  setwd(palmbase)

  saveRDS(LegalPlantationMask, "LegalPlantationMask.rds")
}else{
    setwd(palmbase)
  LegalPlantationMask <- readRDS("LegalPlantationMask.rds")
  }


maskrast<- matrix(1, nrow = 7771, ncol =7611 ) 
maskrast[LegalPlantationMask] <- 0

predmat2 <- predmat

#create a logical mask
predmat2 <- predmat2 * maskrast

#class everything that is platnation but outside the legal zones as 2 everything else = 0
predmat2 <- (predmat2 == 3)*2

#add the two matrices together so that a 6 is the level for conflict palm
predmat2 <- predmat + predmat2
```


```{r PlotConflict}

#compress the new matrix

Catags <- c("Cloud", "Empty", "Forest", "Plantation", "Water", "Conflict")
CatColours <- c("black","white", "darkgreen", "green", "blue", "red")

z <- CompressAndPlot(predmat2, 10, Catags, CatColours)

```



```{r OutputTable}
TypeSplit <- 0:5 %>% map_dbl(~sum(predmat2==.)) %>% data.frame(Pixels=.)  %>%
  mutate(Type = c( "Empty", "Cloud", "Forest", "Plantation", "Water", "Conflict Palm"),
         `Km^2`= round(Pixels *9e-5)
         ) %>% 
  filter(Type != "Empty") %>% 
  select(-Pixels) %>% 
  mutate(`Percent of Total` = round(`Km^2`/sum(`Km^2`)*100))

output<- data_frame(`Percent Conflict` = round(TypeSplit[5,2]/(TypeSplit[3,2]+TypeSplit[5,2])*100),
            `Tonnes Production` = (TypeSplit[3,2]+TypeSplit[5,2])*3.69*100,
            `Tonnes Conflict` = (TypeSplit[5,2])*3.69*100,
            `Value of Conflict (MUSD)` = round((TypeSplit[5,2])*3.69*100 * ppt/1e6))


TypeSplit %>% stargazer(., type="html", summary = FALSE)

output %>% gather() %>% stargazer(., type="text", summary = FALSE)


TypeSplit %>% kable
```

